\chapter{Sprint 4}
\label{chap:S4}

In the fourth sprint of the project the user feedback had been collected from the workshop held in Oslo. The main focus of the sprint was on Pre-delivery efforts both by working on the system development while most of the resources were focused on writing the report. Based upon the user feedback the group made some changes to the design and functionality of the prototype. The group's main goal was getting all the documentation ready for the pre-delivery, while part of the development team worked on the planned Android app. The group had also reached the point where adding more features might be too time consuming. The goal is delivering a fully functioning web page rather than one with many half-working functions.

\subsection{Sprint plan}
\label{subsec:S4Plan}

As the User feedback has been collected from the workshop held in Oslo, the group started working on the suggestions given by users, modifications for the previous system with  some changes in Search Map display, Events should be displayed in the map as well as in the feed when selected, Pictures (and other media) should display some information when selected, like interests, location and maybe the uploader, When registering as a new user you should be automatically logged in, Should have a mobile app that integrates the phone’s camera to enable one-click upload, Enable support for some kind of direct user to user messaging, Consider some way of connecting this to Facebook (sharing photos), Needs some form of reward for use, like meeting new friends and getting feedback when people interact with your content (Like button/user rating),They suggested us the following tips for creating exposure for the product by
Ads on T-banen,
Help from affiliated teenagers,
Cooperation with existing sites focused on youth, Ung Info,
Advertise the qualities that make this product unique,
keep in mind how to stimulate and create user habits to check this thing often.
The users suggested that the current solution for uploading pictures-
Taking a picture in mobile, connecting the mobile to Personal Computer(PC),transferring and uploading the picture into web is very inefficient and off-putting,
Needs system to remove troublesome users: administrators/moderators,
Some way to invite some other users or notify them of an activity in order to not be completely alone if no one comes.
The group considered most of the suggestions and part of the development team started working with the Android app for enabling users to upload a picture into website from the mobile.
The group has decided to make changes with the previous designed webpages for the Map and within the Event Creation page to add a location search map.
There was a session upon the use of youtrack, whole team has been explained upon how to assign the Tasks, estimated hours and fill the hours of work accomplished for particular task and decided to update youtrack by filling up all the previous work of everyone from the team, so the threshold of work will be shown upon the “Burn down chart”.