\chapter{Sprint 1}
In this sprint, the focus is on learning the tools and languages that are required, finishing the analysis and system requirements, and having a good base for the implementation team to continue work on in sprint 2.

\section{Sprint Planning}
The group decided that this sprint would be focused on learning the tools and languages that were needed to complete this project, so that we could shift our focus to implementation in the next sprint. \\
\indent When the sprint is finished, analysis will have been completed, the system requirements will be ready, and we will have a good base to make the next sprint a focused implementation sprint. The implementation for this sprint focuses on adding photo search to the demo, including sorting and tags, and the implementation lead should start thinking about how to split up later tasks.

\section{Duration and Workload}
At the first meeting this sprint we agreed to split the sprints into shorter ones, each lasting one week. \\

\noindent \textbf{Duration: } 14 September - 21 September (1 week)\\
\begin{minipage}{\linewidth}
\setlength{\tabcolsep}{25pt}
\centering
\rowcolors{1}{blue!20}{blue!10}
\begin{tabular}{ |l|l| }
	\hline
	\multicolumn{2}{|c|}{\cellcolor{gray!25} Workload} \\
	\hline
	\it{Analysis} & 11 hrs\\
	\it{System requirements} & 3 hrs\\
	\it{Implementation} & 12 hrs\\
	\it{Testing} & 4 hrs\\
	\it{Learning} & 10 hrs\\
	\it{Documentation} & 5 hrs\\
	\it{Project Management and Meetings} & 32.5 hrs\\
	\hline
	\textbf{\textit{Total Workload}} & 77.5 hrs\\
	\hline
\end{tabular}
%Caption here
\captionof{table}{Workload of Sprint 1.} 
\end{minipage}

\subparagraph{} The group had a plan to work 20-25 hours each this week. We were unable to do this, and only worked approximately 11 hours each. %WRITE DOWN REASONS WHY?

\section{Backlog}
At this point in the project, we had not yet created a backlog to work on. Because of this, we use this section to write what each person planned to do, and for most tasks there is no accuracy to extimated time beyond one week. \\
\begin{minipage}{\linewidth}
\setlength{\tabcolsep}{12pt}
\centering
\rowcolors{1}{blue!20}{blue!10}
\begin{tabular}{|p{1cm}|p{4cm}|p{2cm}|p{2cm}|}
\hline
\cellcolor{gray!25} ID & \cellcolor{gray!25} Description & \cellcolor{gray!25} Estimated Time & \cellcolor{gray!25} Actual Time \\
\hline
N/A & \it{Adding the ability to search for photos on a location-interest coordinate system.} & 1 week & 15 hours \\
N/A & \it{The system requirements still have to be finished} & 1 hour & 1 hour \\
N/A & \it{System development tasks need to be split up and time for each of these estimated} & 1 week & 4 hours \\
\hline
\end{tabular}
\captionof{table}{Backlog for sprint 1.} 
\end{minipage}

\section{Analysis}

\section{Implementation}
In this sprint, most of the implementation team focused on learning or relearning JavaScript, PHP, and CSS. The Technical Lead was the only person working on the system. He spent his time developing a basic system for searching for photos on a location-interest coordinate system, in order to get informed customer feedback about such a system at the earliest opportunity. After finishing that task, he started looking at how to split up later tasks in preparation for creating a backlog next sprint.
\subsection*{Photo Search}


\section{Group Dynamics}

\section{Customer Feedback}

\section{Retrospective}